%\section{Research Design and Methodology}
Read publicly available material of emerging standards and at least three implementations of standards. Create new draft Open API specification that can be used for implementation. Also create reference implementation for ease of its adaptation. 

\par The proposed research work is structured in 4 phases,

\begin{enumerate}
    \item Phase1: Study and Understand emerging standards that are relevant to Self Sovereign Identity (SSI)
    \item Phase2: Study, Understand and evaluate atleast 3 implementation that provides/supports SSI
    \item Phase3: Create Open API Sepcification for implementation that can be adopted for public good
    \item Phase4: Create Reference implementation of defined Open API Specifications
\end{enumerate}

\section{Phase1: Study and Understand emerging standards that are relevant to Self Sovereign Identity (SSI)}
Need to have detailed understanding of below listed relevant emerginig standards that exists around SSI:
\begin{enumerate}
    \item \ac{DIDs} and Verifiable Credentials from the \ac{W3C}
    \item Universal Resolver and Identity Hubs from the \ac{DIF}
    \item DID Auth from the \ac{RWOT} working group
    \item Open Badges from Mozilla and IMS Global
\end{enumerate}
In this phase we will study required specifications, algorithms and  analysis method to learn its strengths and weaknesses. This will help us in analysis in phase2.
Following sections of specifications will be used in our research:
\begin{itemize}
    \item DID Core
    \item DID Use cases and Requirements
    \item DID Specification Registries
    \item DID Core Implementation Report
    \item Verifiable Credentials Data Model
    \item DID Core Specification Test Suite and Implementation Report
    \item \ac{JSON-LD}
    \item Decentralized Identity Foundation Well-Known DID Configuration
    \item Decentralized Identity Foundation DIF Identity Hubs
    \item IMS Global Open Badges
    \item Sovrin
    \item Decentralized Identity Foundation Sidetree Protocol Specification
    \item DID Auth from the Rebooting the Web-of-Trust (RWOT) working group
\end{itemize}

\section{Phase2: Study, Understand and evaluate atleast 3 implementation that provides/supports SSI}
In this phase we will map our understanding and analysis to atleast 3 implementation of SSI specification. At present Jolocom, Sovereign, and Tykn are identified for the same.

\section{Phase3: Create Open API Specification for implementation that can be adopted for public good}
In this phase based on understanding and analysis of the selected 3 implementations, design and create open API specifications that addresses inter-operability, performance and security requirements .

\section{Phase4: Create Reference implementation of defined Open API Specifications}
In this phase create reference implementation of open api specification so that its becomes easier for ecosystem to adapt to these open specification.

Performance and speed measurement matrices will be decisive factors in all our experiments. 
