\section{Paper 10}
    %Begin Table formatting
    \begin{center}
    \begin{tabular}{ | m{5em} | m{25em} |} 
      \hline
      Author(s) Name &  David W. Chadwick;Romain Laborde;Arnaud Oglaza;Remi Venant;Samer Wazan;Manreet Nijjar\\ 
      \hline
      Paper Name &  Improved Identity Management with Verifiable Credentials and FIDO\\ 
      \hline
      Publication Year &  2019\\ 
      \hline
    \end{tabular}
    \end{center}
    %End Table formatting
    In \cite{9031543}, it describes how Fast Identity Online (FIDO) and World Wide Web Consortium (W3C) Verifiable Credentials (VCs) can overcome the problems of existing identity management systems (IDMs). Identity by providing the token for accessing service provider exposes risk of stealing token and could be misused. W3C VC instead is not a token and in w3c model, service providers needs to trust identity providers. Attribute aggregation and fine grained privacy access can be possible. Multiple Verificable Credentials can be used to get required service from service provider. FIDO2 conceptual model and architecture, and the protocol is used by extending FIDO's UAF in order to provide both strong authentication and strong authorization. It also describes a pilot implementation for U.K. NHS patients to validate implementation. Patients were able to use a mobile phone with a fingerprint reader to access restricted NHS sites in order to make and cancel appointments and order repeat prescription drugs. Also the initial user trials with 10 U.K. NHS patients found the system to be easy to use, and fingerprints to be preferable to using usernames and passwords for authentication.